Lexicalized Domain Representations for Neural Machine Translation

### 2019-05-21 2019/emnlp/sparse.tex
add number, shorter introduction

\section{Introduction \label{sec:introduction}}
% The problem
Owing to the development of flexible and powerful architectures based on neural networks \cite{Cho14properties,Bahdanau15learning,Ghering17convolutional,Vaswani17attention}, Machine Translation (MT) has made significant progresses over the past years, and constitute to date the standard for most production engines. One issue which repeatedly pops up with MT, be it neural or statistical, is the need to perform training with large parallel corpora, typically consisting of millions of parallel sentences deemed to be as close as possible to the application domain. A lot of the recent research effort has thus focused on developping MT systems in restricted data conditions, for instance building multilingual MTs which enable zero-shot translation \cite{Firat16multiway,Ha16towards,Johnson17google}; or even building systems without any parallel data \cite{Artetxe18unsupervised,Lample18unsupervised}.
Another important scenario for industrial MT systems is to adapt a neural system trained using parallel data in one domain to the peculiarity of other domains. Domain Adaption (DA) in MT is an old issue \cite{Foster07mixture,Axelrod11domain}, which comes in various guises, and for which a number of solutions have been studied (see the recent survey of \cite{Chu18asurvey} for neural MT). The typical setting is \emph{supervised adaptation}, where a (small) amount of data of the target domain of interest is used to fine-tuned the parameters of a system trained on a large amount of texts in a source domain. We study here a different scenario, \emph{multi-domain adaptation} \cite{Sennrich13multidomain,Farajian17multidomain}, where we would like to use heterogenous data sources to train a unique system that would work well for all domains. This allows us to be both data efficient (all data is used to train all domains) and computationally efficient (we only train one system). In our setting, we assume that the domain of test documents is known.

Multi-domain adaptation is conceptually close to multilingual MT, or more generally to multi-task learning \cite{Caruana97multitask}, and can be approached in a number of ways. We adapt here theideas of \cite{Daume07frustratingly} to neural MT, in an attempt to confine the differences between domains at the lexical level, while the rest of the parameters is shared between domains. Our main hypothesis is that most of the differences between domains take place at the lexical level, due to cross-domain polysemy. By contrast, the deeper layers, which arguably model more abstract linguistic phenomena, are made shareable across domains.
To this end, we make sure to design word embeddings in such that they will contain a generic as well as a domain-specific region. We perform experiments with three domains, two neural architectures and two language pairs and find that our technique can effectively build multi-domain NMT, outperforming several baselines. Our contribution is thus as follows
\begin{itemize}
\item we develop methods to adapt the ideas of \cite{Daume07frustratingly} for two NMT architectures;
\item we provide experimental evidence that suggest the effectiveness of this technique;
\item our analysis of embeddings seems to confort our assumption that their variation across domain actually reflects a variation of senses.
\end{itemize}
\fyDone{can we train in random order ? can we get away with catastrophic forgetting ?}
\fyDone{how to analyze the embeddings ? how can we test or claim ?}

@@

\subsection{Baselines \label{ssec:baselines}}
To validate our findings, we compared lexicalized domain embedding models with standard models using both attentional Recurrent Neural Networks (RNNs) \cite{Bahdanau15learning} and the recent Transformer architecture of \citet{Vaswani17attention}. Our baselines consist of generic models trained with a simple concatenation of all corpora (denoted \texttt{mixed} in the score tables below); models finetuned separately to each domain using (10000, 15000, 5000) iterations over in-domain data (denoted \texttt{+ft(EMEA)}, \texttt{+ft(EPPS)}, \texttt{+ft(ECB)} below); models using domain tags as in \cite{Kobus17domaincontrol} (noted \texttt{DC} below); and finally the multi-domain model of \citet{Zeng18multidomain} (denoted \texttt{WDCMT} below).\fyTodo{Change names in tables}

For all models, we set the size of word embeddings equal to 512; the size of hidden layers is equal to 1024 for RNNs and 512 for Transformer. Other important configuration details that were kept fixed throughout are as follows:
\fyDone{Improve this}
\begin{itemize}
\item Our Transformer models use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 components; 
%  size of word embedding: 512; size of hidden layers: 512; size of inner feed forward layer: 2048; Multi-head: 8; number of layers: 6.
\item Our RNN models use 1 layer on both sides: a bidirectional LSTM encoder and a unidirectional LST decoder with attention;
%  Attention Recurrent Neural Network: Bidirection LSTM encoder, unidirectional LSTM decoder, Luong Attention Mechanism, size of word embedding: 512; size of hidden layers: 1024; number of layers: 1
\item The domain control systems are exactly as their baseline counterpart (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.\fyDone{Check This!}
  % C: size of domain embedding:2 ; same settings for both architecture: Transformer and Attention Recurrent Neural Network.
\item The \texttt{WDCMT} system also has one layer on the encoder side (a bidirectional Gated recurrent units (GRU) layer), as well as one layer on the decoder side (a unidirectional conditional GRU layer); the dimension of ``domain'' layers is~300.
\end{itemize}
To train NMT systems, we use Adam, with parameters $\beta_1=0.9$, $\beta_2 = 0.999$, $\alpha=0.0005$ for RNNs; with parameters $\beta_1=0.9$, $\beta_2= 0.98$, with Noam decay \cite{Vaswani17attention} for Transformer (using $warmup\_steps=4000$). For all systems, we use a batch size of~128 and a dropout rate of 0.1 for all layers. Our implementation is from OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein2017OpenNMT}, except for WDCMT where we use the authors' implementation.\footnote{\noindent\url{http://github.com/DeepLearnXMU/WDCNMT}}\fyDone{batch size}

\subsection{Implementing LDR}\fyTodo{Check acronym.}
\fyTodo{Motivate the split - discuss experimentally embedding size}
For the implementation of lexicalized domain representations, we split the embedding vector (of size 512) into four regions: 3 are domain specific and 1 is generic, with respective sizes $[8,8,8,488]$, a choice that will be dicussed in Section~\ref{secc:region_size}. If a sentence originates from domain $i$, the domain specific regions for all domains $j \neq i$ will be zeroed out; while the other regions are activated (cf. Figure~\ref{fig:network}). We then use a dense layer of size~512 to fuse the region for the active domain and the ``generic'' region. Training is formalized in algorithm~\ref{alg:multidomain}.

@@

For these test sets, our proposal (\texttt{LDR}$_{oracle}$) is consistently better that the mix-domain strategy, with gains that range from very large (for EMEA and ECB) to unsignificant (for EPPS in most conditions). This means that our architecture is somehow able to compensate for the data unbalance and to raise the performance of the multi-domain system close to the best (fine-tuned) system in each domain. We even observe rare cases where the \texttt{LDR}$_{oracle}$ system outperforms fine-tuning (eg.\ Transformer en:ge in the EMEA domain). \texttt{LDR}$_{oracle}$ is also better than Domain Control in three conditions out of four, \texttt{DC} being seemingly a better choice for the RNN than for the Transformer architecture. The comparison with the \texttt{WDCMT} model is less favourable for our RNN systems, which are arguably much simpler.\footnote{The direct comparison with WDCMT is difficult as the implementation differs in many ways from our RNN: a different framework, different cell types (LSTMs vs. conditional GRUs), etc.} \fyDone{More on this.}
As expected, ignoring the domain label yields a drop in performance for the two fallback strategies considered in this study. The first, \texttt{LDR}$_{generic}$, only uses the generic part of the embeddings. The second, \texttt{LDR}$_{pred}$, resorts to automatically predicted domain labels\footnote{Our domain classifier uses a bi-LSTM RNN encoder, followed by a simple softmax layer. Its precision on a development set are higher than 95\%.}
\fyTodo{Explain how} Note that this decrease is however quite limited (and hardly significant for \texttt{LDR}$_{pred}$), showing that our architecture is quite robust to noisy labels. Even in the worst case scenario where all domain tags are intently wrong (\texttt{LDR}$_{wrong}$), we see that the generic part still ensures a satisfying level of performance. A last contrast is with \texttt{LDR}$_{oracle}^{0.5}$ where we change the distribution of training sentence to increase the number of ECB samples: as a result, we see a small decrease for EMEA and EPPS, and a large boost for ECB. This shows that our technique can be used in conjunction to other well known strategies for performing domain adaptation.

@@

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]  
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69$_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & avg \\
\hline
$\mathtt{FT} (EMEA)$ & 76.77$_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & avg \\
$\mathtt{FT} (EPPS)$  & 20.86 & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & avg \\
$\mathtt{FT} (ECB)$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 & avg \\
\hline
$DC$ & 67.87$_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & avg\\
\hline
$LDR_{oracle}$   & 74.26$_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & avg \\
$LDR^{v2}_{oracle}$   & 74.95$_{49.38}$ & 37.35 & 55.91 & 33.57 & 27.59 & 25.27 & avg \\
$LDR_{generic}$ & 73.97$_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & avg \\
$LDR_{pred}$ & 74.29 $_{49.84}$ & 37.73 & 54.01 & 33.34 & 28.32 & 26 & avg \\
$LDR_{wrong}$ & 72.95$_{49.78}$ & 37.62 & 53.35 & - & - & - & avg\\
  \hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English $\rightarrow$German} \\
\hline
$Mixed$ & 64.57$_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 & avg \\
\hline
$\mathtt{FT} (EMEA)$ & 68.35$_{42.97}$ & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & avg\\
$\mathtt{FT} (EPPS)$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & avg \\
$\mathtt{FT} (ECB)$  & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & avg \\
\hline
$DC$ & 63.48$_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & avg \\
\hline
$LDR_{oracle}$ & 70.9$_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & avg \\
$LDR^{v2}_{oracle}$ & 71.31$_{45.23}$ & 25.98 & 73.74 & 21.6 & 16.37 & 19.2 & avg \\
$LDR_{generic}$ & 70.86$_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & avg\\
$LDR_{pred}$ & 70.89$_{46.12}$ & 26.53 & 68.63 & 21.45 & 16.61 & 19.07 & avg \\
$LDR_{wrong}$ & 69.51$_{43.50}$ & 26.31 & 66.86 & - & - & - & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture \label{tab:results-trsf}}
\end{table*}

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$               & 65.42$_{45.11}$ & 34.7 & 51.38 & 29.27 & 22.21 & 21.63 & avg \\
\hline
$\mathtt{FT} (EMEA)$  & 72.06 $ $ & 18.62 & 16.78 & 25.88 & 10.94 & 5.73 & avg \\
$\mathtt{FT} (EPPS)$    & 35.47 $ $ & 34.61 & 39.56 & 27.11 & 21.85 & 20.61 & avg \\
$\mathtt{FT} (ECB)$     & 21.93 $ $ & 22.6 & 51.53 & 14.74 & 12.10 & 10.47 & avg \\
\hline
$DC$                   & 68.26 $_{43.76}$ & 35.13 & 50.09 & 27.86 & 20.95 & 21.16 & avg \\
 \hline
$WDCMT$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & 32.03 & 24.63 & 23.28 & avg \\
\hline
$LDR_{oracle}$   & 71.73 $_{46.30}$ & 35.21 & 50.91 & 29.62 & 23.00 & 20.96 & avg\\
$LDR_{generic}$ & 70.59 $_{46.37}$ & 35.22 & 49.68 & 29.51 & 23.00 & 20.96 & avg\\
$LDR_{pred}$        & 72.76 $_{46.35}$ & 35.1 & 50.38 & 30.02 & 23.28 & 21.32 & avg\\
$LDR_{wrong}$   & 62.1 $_{43.29}$ & 34.17 & 48.79 &  - & - & - & avg \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$               & 57.37 $_{37.94}$ & 23.1 & 63.54 & 17.39 & 11.51 & 14.29 & avg\\
\hline
$\mathtt{FT} (EMEA)$  & 65.64$_{44.71}$ & 12.36 & 15.93 & 15.38 & 6.22 & 7.6  & avg\\
$\mathtt{FT} (EPPS)$   & 24.90 $ $ & 22.98 & 26.26 & 13.55 & 11.33 & 14.32 & avg \\
$\mathtt{FT} (ECB)$    & 41.8 $ $ & 15.97 & 71.07 & 10.77 & 7.66 & 8.07 & avg\\
\hline
$DC$                    & 62.53 $_{39.25}$ & 23.74 & 65.71 & 16.88 & 11.15 & 14.97 & avg\\
\hline
WDCMT               & 64.05 $_{38.54}$ & 22.82 & 67.00 & 15.94 & 11.45 & 13.66 & avg\\
\hline
$LDR_{oracle}$   & 63.43 $_{40.04}$ & 22.66 & 64.40 & 16.99 & 11.45 & 14.26 & avg\\
$LDR^{v2}_{oracle}$   & 63.27 $_{38.16}$ & 21.83 & 69.55 & 15.7 & 11.32 & 13.98 & avg\\
$LDR_{generic}$ & 63.27 $_{39.75}$ & 22.62 & 63.70 & 17.26 & 11.45 & 14.26 & avg\\
$LDR_{pred}$        & 63.17 $_{39.92}$ & 22.51 & 64 & 15.94 & 11.32 & 14.27 & avg\\
$LDR_{wrong}$   & 56.84 $_{37.05}$ & 22.06 & 61.66 & - & - & - & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN architecture \label{tab:results-rnn}}
\end{table*}
% \clearfloat

@@

\section*{Acknowledgments}
\fyTodo{Homegenize refs - urls, addresses, etc}
\bibliography{emnlp-ijcnlp-2019}
\bibliographystyle{acl_natbib}
\end{document}

>>>>

\section{Introduction \label{sec:introduction}}
% The problem
Owing to the development of flexible and powerful architectures based on neural networks \cite{Cho14properties,Bahdanau15learning,Ghering17convolutional,Vaswani17attention}, Machine Translation (MT) has made significant progresses over the past years, and constitute to date the standard for most production engines. The development of MT systems, be they neural or statistical, require very large parallel corpora consisting of millions of sentence pairs, a resource that only exist in very few application domains and language pairs. A lot of the recent research effort has thus focused on developping MT systems in restricted data conditions, for instance building multilingual MTs which enable zero-shot translation \cite{Firat16multiway,Ha16towards,Johnson17google}; or even building systems without any parallel data \cite{Artetxe18unsupervised,Lample18unsupervised}.
Another important scenario for industrial MT is to adapt a neural system trained using parallel data in one domain to the peculiarity of other domains. Domain Adaption (DA) in MT is an old issue \cite{Foster07mixture,Axelrod11domain}, which comes in various guises, and for which a number of solutions have been studied (see the recent survey of \cite{Chu18asurvey} for neural MT). The typical setting is \emph{supervised adaptation}, where a (small) amount of data of the target domain of interest is used to fine-tuned the parameters of a system trained on a large amount of texts in a source domain. We study here a different scenario, \emph{multi-domain adaptation} \cite{Sennrich13multidomain,Farajian17multidomain}, where we would like to use heterogenous data sources to train a unique system that would work well for all domains. This allows us to be both data efficient (all data is used to train all domains) and computationally efficient (we only train one system). In our setting, we assume that the domain of test documents is known.

Multi-domain adaptation is conceptually close to multilingual MT, or more generally to multi-task learning \cite{Caruana97multitask}, and can be approached in a number of ways. We adapt here ideas of \citet{Daume07frustratingly} to neural MT, in an attempt to confine the differences between domains at the lexical level, while the rest of the parameters is shared between domains. Our main hypothesis is that most of the differences between domains take place at the lexical level, due to cross-domain polysemy. By contrast, the deeper layers, which arguably model more abstract linguistic phenomena, are made shareable across domains.
To this end, we design word embeddings made of a generic as well as several domain-specific regions. We perform experiments with three domains, two neural architectures and two language pairs and find that our technique can effectively build multi-domain NMT, outperforming several baselines. Our contribution is thus as follows:
\begin{itemize}
\item we implement the ideas of \cite{Daume07frustratingly} for two NMT architectures;
\item we provide experimental evidence that suggest the effectiveness of this technique;
\item our analysis of embeddings seems to confort our assumption that their variation across domain actually reflects a variation of senses.
\end{itemize}
\fyDone{can we train in random order ? can we get away with catastrophic forgetting ?}
\fyDone{how to analyze the embeddings ? how can we test or claim ?}

@@

\subsection{Baselines \label{ssec:baselines}}
To validate our findings, we compared lexicalized domain embedding models with standard models using both attentional Recurrent Neural Networks (RNNs) \cite{Bahdanau15learning} and the recent Transformer architecture of \citet{Vaswani17attention}. Our baselines consist of generic models trained with a simple concatenation of all corpora (denoted \texttt{mMixed} in the tables below); models tuned separately on each domain using respectively (10000, 15000, 5000) iterations over in-domain data (denoted \texttt{+ft(EMEA)}, \texttt{+ft(EPPS)}, \texttt{+ft(ECB)} below); models using domain tags as in \cite{Kobus17domaincontrol} (\texttt{DC} below); and finally the multi-domain model of \citet{Zeng18multidomain} (\texttt{WDCMT} below).\fyDone{Change names in tables}
For all models, we set the embeddings size equal to 512; the size of hidden layers is equal to 1024 for RNNs and 512 for Transformer. Other important configuration details are as follows:
\fyDone{Improve this}
\begin{itemize}
\item Transformer models use multi-head attention with 8 heads in each of the 6 layers; the inner feedforward layer contains 2048 cells; 
%  size of word embedding: 512; size of hidden layers: 512; size of inner feed forward layer: 2048; Multi-head: 8; number of layers: 6.
\item RNN models use 1 layer on both sides: a bidirectional LSTM encoder and a unidirectional LSTM decoder with attention;
%  Attention Recurrent Neural Network: Bidirection LSTM encoder, unidirectional LSTM decoder, Luong Attention Mechanism, size of word embedding: 512; size of hidden layers: 1024; number of layers: 1
\item The domain control systems are exactly as their baseline counterparts (RNN and Transformer), with an additional 2 cells encoding the domain on the input layer.\fyDone{Check This!}
  % C: size of domain embedding:2 ; same settings for both architecture: Transformer and Attention Recurrent Neural Network.
\item The \texttt{WDCMT} system has one bidirectional Gated recurrent units (GRU) layer on the encoder side and one unidirectional conditional GRU layer on the decoder side; the dimension of ``domain'' layers is~300.
\end{itemize}
To train NMT systems, we use Adam, with parameters $\beta_1=0.9$, $\beta_2 = 0.999$, $\alpha=0.0005$ for RNNs; with parameters $\beta_1=0.9$, $\beta_2= 0.98$, with Noam decay \cite{Vaswani17attention} for Transformer (using $warmup\_steps=4000$). For all systems, we use a batch size of~128 and a dropout rate of 0.1 for all layers. Our implementation is from OpenNMT-tf\footnote{\url{https://github.com/OpenNMT/OpenNMT-tf}} \cite{Klein2017OpenNMT}, except for WDCMT where we use the authors' implementation.\footnote{\noindent\url{http://github.com/DeepLearnXMU/WDCNMT}}\fyDone{batch size}

\subsection{Implementing LDR}\fyTodo{Check acronym.}
\fyDone{Motivate the split - discuss experimentally embedding size}
For the implementation of lexicalized domain representations, we split the embedding vector (of size 512) into four regions: 3 are domain specific and 1 is generic, with respective sizes $[8,8,8,488]$, a choice that will be dicussed in Section~\ref{secc:region_size}. If a sentence originates from domain $i$, the domain specific regions for all domains $j \neq i$ will be zeroed out; while the other regions are activated (cf. Figure~\ref{fig:network}). We then use a dense layer of size~512 to fuse the region for the active domain and the ``generic'' region. Training is formalized in algorithm~\ref{alg:multidomain}.

@@

For these test sets, our proposal (\texttt{LDR}$_{oracle}$) is consistently better that the mix-domain strategy, with gains that range from very large (for EMEA and ECB) to unsignificant (for EPPS in most conditions). This means that our architecture is somehow able to compensate for the data unbalance and to raise the performance of the multi-domain system close to the best (fine-tuned) system in each domain. We even observe rare cases where the \texttt{LDR}$_{oracle}$ system outperforms fine-tuning (eg.\ Transformer en:ge in the EMEA domain). \texttt{LDR}$_{oracle}$ is also better than Domain Control in three conditions out of four, \texttt{DC} being seemingly a better choice for the RNN than for the Transformer architecture. The comparison with the \texttt{WDCMT} model is less favourable for our RNN systems, which are arguably much simpler.\footnote{The direct comparison with WDCMT is difficult as the implementation differs in many ways from our RNN: a different framework, different cell types,
  % (LSTMs vs. conditional GRUs),
  etc.} \fyDone{More on this.}
As expected, ignoring the domain label yields a drop in performance for the two fallback strategies considered in this study. The first, \texttt{LDR}$_{generic}$, only uses the generic part of the embeddings. The second, \texttt{LDR}$_{pred}$, resorts to automatically predicted domain labels\footnote{Our domain classifier uses a bi-LSTM RNN encoder, followed by a simple softmax layer. Its precision on a development set are higher than 95\%.}
\fyTodo{Explain how} Note that this decrease is however quite limited (and hardly significant for \texttt{LDR}$_{pred}$), showing that our architecture is quite robust to noisy labels. Even in the worst case scenario where all domain tags are intently wrong (\texttt{LDR}$_{wrong}$), we see that the generic part still ensures a satisfying level of performance. A last contrast is with \texttt{LDR}$_{oracle}^{0.5}$ where we change the distribution of training sentence to increase the number of ECB samples: as a result, we see a small decrease for EMEA and EPPS, and a large boost for ECB. This shows that our technique can be used in conjunction to other well known strategies for performing domain adaptation.

@@

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]  
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69$_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & 41.3\\
\hline
$\mathtt{FT} (EMEA)$ & 76.77$_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & 26.37 \\
$\mathtt{FT} (EPPS)$  & 20.86 & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & 25.62 \\
$\mathtt{FT} (ECB)$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 &  27.35\\
\hline
$DC$ & 67.87$_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & 40.71\\
\hline
$LDR_{oracle}$   & 74.26$_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & 42.28\\
$LDR^{v2}_{oracle}$   & 74.95$_{49.38}$ & 37.35 & 55.91 & 33.57 & 27.59 & 25.27 & 42.44\\
$LDR_{generic}$ & 73.97$_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & 42.24 \\
$LDR_{pred}$ & 74.29 $_{49.84}$ & 37.73 & 54.01 & 33.34 & 28.32 & 26 & 42.28\\
$LDR_{wrong}$ & 72.95$_{49.78}$ & 37.62 & 53.35 & - & - & - & - \\
  \hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English $\rightarrow$German} \\
\hline
$Mixed$ & 64.57$_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 &36.23 \\
\hline
$\mathtt{FT} (EMEA)$ & 68.35$_{42.97}$ & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & 27.35\\
$\mathtt{FT} (EPPS)$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & 31.42\\
$\mathtt{FT} (ECB)$  & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & 25\\
\hline
$DC$ & 63.48$_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & 35.56\\
\hline
$LDR_{oracle}$ & 70.9$_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & 37.15\\
$LDR^{v2}_{oracle}$ & 71.31$_{45.23}$ & 25.98 & 73.74 & 21.6 & 16.37 & 19.2 & 38.03\\
$LDR_{generic}$ & 70.86$_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & 37.14\\
$LDR_{pred}$ & 70.89$_{46.12}$ & 26.53 & 68.63 & 21.45 & 16.61 & 19.07 & 32.2 \\
$LDR_{wrong}$ & 69.51$_{43.50}$ & 26.31 & 66.86 & - & - & - & - \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer systems \label{tab:results-trsf}}
\end{table*}

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$               & 65.42$_{45.11}$ & 34.7 & 51.38 & 29.27 & 22.21 & 21.63 &37.43 \\
\hline
$\mathtt{FT} (EMEA)$  & 72.06$_{47.33}$ & 18.62 & 16.78 & 25.88 & 10.94 & 5.73 & 20 \\
$\mathtt{FT} (EPPS)$    & 35.47 $ $ & 34.61 & 39.56 & 27.11 & 21.85 & 20.61 & 29.87 \\
$\mathtt{FT} (ECB)$     & 21.93 $ $ & 22.6 & 51.53 & 14.74 & 12.10 & 10.47 & 22.23 \\
\hline
$DC$                   & 68.26 $_{43.76}$ & 35.13 & 50.09 & 27.86 & 20.95 & 21.16 & 37.24\\
 \hline
$\mathtt{WDCMT}$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & 32.03 & 24.63 & 23.28 & 38.97 \\
\hline
$LDR_{oracle}$   & 71.73 $_{46.30}$ & 35.21 & 50.91 & 29.62 & 23.00 & 20.96 & 38.57\\
$LDR^{v2}_{oracle}$   & 63.27 $_{38.16}$ & 21.83 & 69.55 & 15.7 & 11.32 & 13.98 & 32.6\\
$LDR_{generic}$ & 70.59 $_{46.37}$ & 35.22 & 49.68 & 29.51 & 23.00 & 20.96 & 38.16\\
$LDR_{pred}$        & 72.76 $_{46.35}$ & 35.1 & 50.38 & 30.02 & 23.28 & 21.32 & 38.81\\
$LDR_{wrong}$   & 62.1 $_{43.29}$ & 34.17 & 48.79 &  - & - & - & - \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$               & 57.37 $_{37.94}$ & 23.1 & 63.54 & 17.39 & 11.51 & 14.29 & 31.2\\
\hline
$\mathtt{FT} (EMEA)$  & 65.64$_{44.71}$ & 12.36 & 15.93 & 15.38 & 6.22 & 7.6  & 20.53\\
$\mathtt{FT} (EPPS)$   & 24.90 $ $ & 22.98 & 26.26 & 13.55 & 11.33 & 14.32 & 18.89 \\
$\mathtt{FT} (ECB)$    & 41.8 $ $ & 15.97 & 71.07 & 10.77 & 7.66 & 8.07 & 25.89\\
\hline
$DC$                      & 62.53 $_{39.25}$ & 23.74 & 65.71 & 16.88 & 11.15 & 14.97 & 32.50\\
\hline
$\mathtt{WDCMT}$ & 64.05 $_{38.54}$ & 22.82 & 67.00 & 15.94 & 11.45 & 13.66 & 32.49\\
\hline
$LDR_{oracle}$   & 63.43 $_{40.04}$ & 22.66 & 64.40 & 16.99 & 11.45 & 14.26 & 32.2\\
$LDR^{v2}_{oracle}$   & 63.27 $_{38.16}$ & 21.83 & 69.55 & 15.7 & 11.32 & 13.98 & 32.6\\
$LDR_{generic}$ & 63.27 $_{39.75}$ & 22.62 & 63.70 & 17.26 & 11.45 & 14.26 & 32.1\\
$LDR_{pred}$        & 63.17 $_{39.92}$ & 22.51 & 64 & 15.94 & 11.32 & 14.27 & 31.87\\
$LDR_{wrong}$   & 56.84 $_{37.05}$ & 22.06 & 61.66 & - & - & - & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN systems\label{tab:results-rnn}}
\end{table*}
% \clearfloat

@@

%\section*{Acknowledgments}
% \fyTodo{Homegenize refs - urls, addresses, etc}
\bibliography{emnlp-ijcnlp-2019}
\bibliographystyle{acl_natbib}
\end{document}
